Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-06 article.tex
Use booktabs for tbale

 %\usepackage{rotating}% for sideways figures and tables
\usepackage{longtable}% for long tables

@@

\paragraph{Improvement of each stage of our approach\\}

\begin{table}[htb]
\centering
\begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
1 & Inverse correlation & & & & \\ \hline
2 & Pre-processing & & & &\\ \hline
3 & PCA & & & &  \\ \hline
4 & Weighting & & & &  \\ \hline
5 & Averaging & & & &  \\ \hline

\end{tabular}
\end{table}

Note that we choose the \textit{best} threshold for stages 1 to 4.
\paragraph{Comparison with other methods\\}

\begin{table}[htb]
\centering
\begin{tabular}{|c|c||c|c|c|c|} \hline
\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
1 & Inverse correlation & & & &\\ \hline
2 & Correlation & & & &\\ \hline
3 & GENIE3 & & & & \\ \hline
4 & GTE & & & & \\ \hline
\end{tabular}
\end{table}
\subsection{Discussion about the metric}
\label{sec:metric}

>>>>

 %\usepackage{rotating}% for sideways figures and tables
% \usepackage{longtable}% for long tables

@@

\begin{table}[htb]
\centering
\caption{Improvement of each stage of our approach Note that we choose the
         \textit{best} threshold for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Inverse correlation & & & & \\
Pre-processing      & & & & \\
PCA                 & & & & \\
Weighting           & & & & \\
Averaging           & & & & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[htb]
\centering
\caption{Comparison with other methods}
\begin{tabular}{*{5}{l}}
\toprule
Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Correlation         & & & & \\
Partial correlation & & & & \\
Our approach        & & & & \\
GENIE3              & & & & \\
GTE                 & & & & \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Discussion about the metric}
\label{sec:metric}
